Rarefy Timeseries

### 2021-10-25 analysis/02_rarefy_timeseries.Rmd

>>>>

Get cwm's that were excluded
Functions to calculate functional diversity metrics for the samples
```{r}
#helper function to load file
loadRData <- function(file_name){
  load(file_name)
  get(ls()[ls() != "file_name"])
}

#function to calculate functional diversity metrics for a single sample community
calc_cwm_mets <- function(file_path, traits){
  #library(biodivTS)
  #load community sample
  rare_comm_save <- loadRData(file_path)

  #get species matrix
  species_mat <- rare_comm_save %>%
    tibble::column_to_rownames("YEAR") %>%
    dplyr::select(-c(rarefyID, cell, type, rarefy_resamp))

  # get trait matrix for the species in the sample
  traits <- biodivTS::get_traitMat(colnames(species_mat), trait_data = traits)

  # create FD function that returns an empty dataframe instead of erroring if FD can't be calculated
  get_FD_safe <- possibly(biodivTS::get_FD, otherwise = data_frame())

  # calculate functional diversity for different data types
  if(unique(rare_comm_save$type) == "count"){
    FD_mets <- get_FD_safe(species_mat = species_mat, trait_mat = traits, year_list = years,
                           data_id = unique(rare_comm_save$rarefyID), 
                           samp_id = unique(rare_comm_save$rarefy_resamp),
                           w.abun = TRUE, m = "min", corr = "cailliez",
                           calc.FDiv = FALSE)
  } else{
    FD_mets <- get_FD_safe(species_mat = species_mat, trait_mat = traits, year_list = years,
                           data_id = unique(rare_comm_save$rarefyID), 
                           samp_id = unique(rare_comm_save$rarefy_resamp),
                           w.abun = FALSE, m = "min", corr = "cailliez",
                           calc.FDiv = FALSE)
  }

  #check if FD metrics could be calculated, otherwise return empty dataframe
  if (is.null(dim(FD_mets))){

    # combine univariate and turnover metrics
    cwm_metrics <- FD_mets$fd_met %>%
      select(year, starts_with("CWM")) %>%
      mutate(cell = unique(rare_comm_save$cell), rarefy_resamp = unique(rare_comm_save$rarefy_resamp)) %>%
      rename(YEAR = year)

  }else{ cwm_metrics <- tibble() }

  #save out dataframe of rarefied metrics
  path <- here::here("data", "rarefied_metrics", "cwm")
  dir.create(path)
  save(cwm_metrics, file=paste0(path, "/", unique(rare_comm_save$type),
                                      "_cell", unique(rare_comm_save$rarefyID),
                                      "_sample", unique(rare_comm_save$rarefy_resamp), ".rda"))

#parallelized mapping across files to calculate functional diversity metrics
future::plan("multiprocess", workers = 30)
furrr::future_map(files, calc_cwm_mets, traits = trait_ref)
```
